---
title: "code"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## problem 

```{r}
print("hello world")

```


## problem 

function that prints prints squares of a sequence of numbers

```{r}
new.function <- function(a) {
  for(i in 1:a) {
    b<- i^2
    print(b)
  }
}

new.function(3)
```



## function without argument

```{r}
new.function <- function() {
  a <- 8
  for(i in 1:a) {
    b<- i^2
    print(b)
  }
}

new.function()
```


## calling function with different argument values

```{r}
new.function <- function(a,b,c) {
  result <- a+2*b + c
  print(result)
}

new.function(1,2,3)
```



## for loop

```{r}
for (i in 1:10) print(i)
```


## lapply the function random_unif to a list of 4 numbers with min =0 and max = 1

```{r}
x <- 1:4
lapply(x, runif, min = 0, max = 1)
```



## sapply does the same thing but simplifys the results

```{r}
x <- 1:4
sapply(x, runif, min = 0, max = 1)
```

## for loop in a function. for 1-10, print each number

```{r}
function_compute <- function(x) {
  for(i in 1:x) {
    if(i < 10) print(i)
  }
}
function_compute(9)

```



## for loop in a function. for 1-10, print just one number

```{r}
function_compute <- function(x) {
  for(i in 1:x) {
    if(i < 10) count = i+1
  }
  print(count)
}
function_compute(9)

```


## for loop that populates a data frame

```{r}

iterations = 10
variables = 2

output = matrix(ncol = variables, nrow = iterations)

for (i in 1:iterations){
  output[i,] <- runif(2)
}

output

```




## function that populates a data frame

```{r}

## because runif(#) returns that number inside of the parentehses
iterations = 2
variables = 4

output = matrix(ncol = variables, nrow = iterations)

for (i in 1:iterations){
  output[i,] <- runif(4)
}

output

```



## function that puts vectors into a list

```{r}
mylist <- list()

for (i in 1:9) {
  for (j in 1:5){
    vec[j] <- i
  }
  mylist[[i]] <- vec
}

mylist
```

## print "hello world" n times

```{r}

for (i in 1:10) {
  print("hello")
}

```




## print "fuzz" for divided by 5 and 3, another word for divisible by 3, and i for the rest 

```{r}
fizzBuzz <- function(n) {
  for (i in 1:n)
    if(i %% 3  == 0 & i %% 5 == 0) {
      return("FizzBuzz")
    } else if (i %% 3 ==0) {
      print("buss")
    } else if (i %%5 == 0) {
      print("fizz")
    } else {
      print("no")
    }
}
fizzBuzz(15)

```





## make a data frame with observations and then find the maximum

```{r}
## this might all be wrong
q = data.frame(region = c("north", "south", "west", "west"), salary = c(5,10,15, 20), 
               employee = c("Mark", "Anthony", "Jared", "Oak"))

colMax <- function(q) sapply(q, max, na.rm = TRUE)
colMax(q)

create_sale_summary_report <- function(df_data) {
  col_max_function <- function(q) sapply(q, max, na.rm = TRUE)
  max_frame <- col_max_function(df_data)
  return(max_frame)
}
create_sale_summary_report(q)

```




## find the average value grouped by each region and pring that

```{r}
q$salary <- as.numeric(q$salary)
aggregate(q[, 2], list(q$region), mean)

```

